R submission Pilots to FDA

### 2023-06-06 slides/china-r.Rmd
fix brocken link
Built site for gh-pages

Training: [December 6th, Deming Conference 2021](https://demingconference.org/wp-content/uploads/2021/07/2021-Deming-Conference-Printed-Program-v1.0.pdf)

@@

More details: <https://r4csr.org/manage.html>

>>>>

Training: [December 6th, Deming Conference 2021](https://web.archive.org/web/20220531042701/https://demingconference.org/wp-content/uploads/2021/11/2021-Deming-Conference-Virtual-Printed-Program-v1.1.pdf)

@@

More details: <https://r4csr.org/project-management.html>

### 2023-06-06 slides/fda-workshop-slides.Rmd
Built site for gh-pages

<https://r4csr.org/population.html>

@@

<https://r4csr.org/baseline-characteristics.html>

@@

<https://r4csr.org/aesummary.html>

@@

<https://r4csr.org/manage.html>

@@

- The R submission working group is a cross-industry pharma working group focusing on improving practices of R-based clinical trial regulatory submission.
  - [members and affiliations](https://rconsortium.github.io/submissions-wg/)
- Mission: Easier R-based clinical trial regulatory submissions
- [pilot 1 - common analyses](https://rconsortium.github.io/submissions-wg/pilot-overall.html#pilot-1---common-analyses)
  - 2021.11   Initial submission to FDA. 
  - 2022.12   Received FDA response 
  - 2022.02   Revised submission to FDA
  - 2022.03   Received final FDA response.

@@

- "Using R version 4.1.1, FDA was able to run the submitted code and confirm the applicant's tables and the submitted figure in report-tlf pdf file."
- "Using FDA developed code, a statistical analyst was able to independently generate tables using the submitted data."
- [Initial submission FDA response](https://github.com/RConsortium/submissions-wg/blob/main/Documents/Summary_R_Pilot_Submission.pdf)

@@

- FDA agrees that the initial phase of the R Pilot submission has been completed.
- [Revised  submission FDA response](https://github.com/RConsortium/submissions-wg/blob/main/Documents/Summary_R_Pilot_Submission2.pdf)

@@

<https://r4csr.org/running-environment.html>

>>>>

<https://r4csr.org/tlf-population.html>

@@

<https://r4csr.org/tlf-baseline.html>

@@

<https://r4csr.org/tlf-ae-summary.html>

@@

<https://r4csr.org/project-management.html>

@@

- The R submission working group is a cross-industry pharma working group focusing on improving practices of R-based clinical trial regulatory submission.
  - [members and affiliations](https://rconsortium.github.io/submissions-wg/)
- Mission: Easier R-based clinical trial regulatory submissions
- [pilot 1 - common analyses](https://rconsortium.github.io/submissions-wg/pilot1.html)
  - 2021.11   Initial submission to FDA. 
  - 2022.12   Received FDA response 
  - 2022.02   Revised submission to FDA
  - 2022.03   Received final FDA response.

@@

- "Using R version 4.1.1, FDA was able to run the submitted code and confirm the applicant's tables and the submitted figure in report-tlf pdf file."
- "Using FDA developed code, a statistical analyst was able to independently generate tables using the submitted data."
- [Initial submission FDA response](https://github.com/RConsortium/submissions-wg/blob/main/_Documents/Summary_R_Pilot_Submission.pdf)

@@

- FDA agrees that the initial phase of the R Pilot submission has been completed.
- [Revised  submission FDA response](https://github.com/RConsortium/submissions-wg/blob/main/_Documents/Summary_R_Pilot_Submission2.pdf)

@@

<https://r4csr.org/submission-environment.html>

### 2023-06-06 slides/r4csr-gwu.Rmd
Built site for gh-pages

- "Using R version 4.1.1, FDA was able to run the submitted code and confirm the applicant's tables and the submitted figure in report-tlf pdf file."
- "Using FDA developed code, a statistical analyst was able to independently generate tables using the submitted data."
- [Original FDA response](https://github.com/RConsortium/submissions-wg/blob/main/Documents/Summary_R_Pilot_Submission.pdf)

>>>>

- "Using R version 4.1.1, FDA was able to run the submitted code and confirm the applicant's tables and the submitted figure in report-tlf pdf file."
- "Using FDA developed code, a statistical analyst was able to independently generate tables using the submitted data."
- [Original FDA response](https://github.com/RConsortium/submissions-wg/blob/main/_Documents/Summary_R_Pilot_Submission.pdf)

### 2023-06-06 slides/r4csr-psi.Rmd
Built site for gh-pages

- Objective: Create open source example for R-based clinical trial regulatory submissions
- [pilot 1 - common analyses](https://rconsortium.github.io/submissions-wg/pilot-overall.html#pilot-1---common-analyses)
  - 2021.11   Initial submission to FDA. 
  - 2022.12   Received FDA response 
  - 2022.02   Revised submission to FDA
  - 2022.03   Received final FDA response.

@@

- [pilot 3 - ADaM data](https://github.com/RConsortium/submissions-wg/blob/main/Documents/R%20Submission%20%20Pilot%201%20Extension%20Proposal.pdf)
  - 2022.10   Proposal initiation.

>>>>

- Objective: Create open source example for R-based clinical trial regulatory submissions
- [pilot 1 - common analyses](https://rconsortium.github.io/submissions-wg/pilot1.html)
  - 2021.11   Initial submission to FDA. 
  - 2022.12   Received FDA response 
  - 2022.02   Revised submission to FDA
  - 2022.03   Received final FDA response.

@@

- [pilot 3 - ADaM data](https://github.com/RConsortium/submissions-wg/blob/main/_Documents/R%20Submission%20%20Pilot%201%20Extension%20Proposal.pdf)
  - 2022.10   Proposal initiation.
